### 2015-11-13 postdoctoral/gamma_functions.tex
generalize clontz-varagona result to comp conn LOTS

@@

  Note that \(\check L\)
  is not a ``compactification'' as \(L\) does not necessarily
  embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
  \(t\mapsto [0,t)\), but then note that the subspace topology induces the
  reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
  However \(\hat L\) is
  the typical way of compactifying a linearly ordered space \(L\),
  provided \(L\) lacks a least element (otherwise the empty set is an [easily
  removable] isolated point in \(\hat L\)). Note that we \textbf{always}
  assume that \(\emptyset\in\hat L\):

  \begin{example}
    \(\hat I\cong\{-\infty\}\cup I\) where
    \(\emptyset\mapsto-\infty\) and \([0,t]\mapsto t\).
  \end{example}

@@

>>>>

  \begin{definition}
    A u.s.c. map \(f\subseteq X^2\)
    satisfies condition \(\Gamma\) if there exists \(x,y\in X\) such that
    \(\<x,x\>,\<y,y\>,\<x,y\>\in f\).
  \end{definition}

  \begin{theorem}
    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
  \end{theorem}

  This was proven in \cite{CLONTZVARAGONA} for the case \(M\) is a closed
  interval of real numbers; however, the same proof applies to this more
  general case.

@@

  Note that \(\check L\)
  is not a ``compactification'' in the usual sense of word
  as \(L\) does not necessarily
  embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
  \(t\mapsto [0,t)\), but then note that the subspace topology induces the
  reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
  However \(\hat L\) is
  the typical way of compactifying a linearly ordered space \(L\),
  provided \(L\) lacks a least element (otherwise the empty set is an [easily
  removable] isolated point in \(\hat L\)). Note that we \textbf{always}
  assume that \(\emptyset\in\hat L\):

  \begin{example}
    \(\hat I\cong\{-1\}\cup [0,1]\) where
    \(\emptyset\mapsto-1\) and \([0,t]\mapsto t\).
  \end{example}

@@

  \begin{corollary}
    If \(f\) is a nontrivial V-map
    and \(K\) is a compact connected LOTS, then
    \(\varprojlim \{K, f, L\}\) is metrizable if and only if
    \(K=I\) and \(L\) is countable.
  \end{corollary}

  \begin{proof}
    \(I\) is the only nontrivial compact connected metrizable LOTS, and all V-maps
    on compact connected LOTS satisfy condition \(\Gamma\).
  \end{proof}
